An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-10 poly-embed-journal/poly-embed-journal.tex
Tinkering with phase 1 of lemma X

\jessie{Lemma X}
\begin{lemma}
	Let $f: \simplex \to \reals_+$ be a (concave) polyhedral function.
	There exists a unique set of loss vectors $\V$ of minimum cardinality such that $f(p) = \min_{v \in \V} \inprod{v}{p}$ for all $p\in\simplex$.
	Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V\}$.
	Furthermore, let $L: \R \to \reals^\Y_+$ be any loss with Bayes risk $\risk L=f$ and let $\Gamma := \prop{L}$.
	Then $L$ has a finite minimum representative set, and for any minimum representative set $\R^* \subseteq \R$,
	\begin{enumerate}
		\item $\{L(r^*) \mid r^* \in \R^*\} = \V$,
		\item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$\jessie{relative to $\reals^{n-1}$},
		\item For any $r \in \R$, there exists $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$\jessie{power diagrams stuff}.
	\end{enumerate}
\end{lemma}

@@

\begin{itemize}\setlength{\itemsep}{0pt}
	\item By Rockafellar, we have $f$ polyhedral if and only if it can be written as the max of a finite set of linear functions $\hat \V$ over $\reals^\Y_+$.%; outside $\reals^\Y_+$, we take $f$ to be infinite.
	Therefore, $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ over $p \in \reals_+^\Y$.
	%Write $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ for some finite set $\hat\V \subseteq \reals^\Y_+$.    \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar}
	\item We extend $f$ to $g(x) = \min_{v\in\hat\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = \infty$ otherwise, and define $g(0) = 0$.
	That is, $g(x) = \min_{v \in \hat \V} \inprod{x}{v} + \delta(x \mid \reals^\Y_+)$.
	Note that $g$ and $f$ match on $\reals^\Y_+$.
	\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ as the hypograph of $g$.
	\item Let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$ as the set of halfspaces generated by $\hat \V$ and $H_{v} := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c = 0\}$ and as the hyperplanes defining the boundaries of these halfspaces.
	\item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$ as the half spaces generated by the nonnegative orthant and $H_y := \{ (x,c) \in \reals^\Y \times \reals \mid x_y = 0\}$ as the hyperplanes forming the boundary of these halfspaces.
	\item Let $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\hat \V} \cup \H_\Y$.
	\item Then $G = \cap \H$.
	\item Since $G$ is a full-dimensional polyhedron, it has a unique $H$-rep $H'$ uniquely determined by the facets of $G$ by \jessie{Ziegler Theorem 2.15}.
	\item Take $\H' := \{(x,c) \mid \inprod{h'}{x} - c \geq 0\}$ for all $h' \in H'$.
	\item Argue $\H' \subseteq \H$ and $G = \cap \H'$. 
	\jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from text linked above}
	\item Argue $\H_\Y \subseteq \H'$.
	\item Then $\H' \setminus \H_\Y = \{H_v^+ : v\in\V\} =: \H_\V$ for some $\V \subseteq \hat \V$.
	\item That's the $\V$ we are looking for.  (And we've argued that it's uniquely determined by $f$.) \jessie{Why is $\V$ minimum cardinality?}
	\item Moreover, $F_v := H_v^+ \cap G$ is a facet of $G$ for each $v\in\V$. \jessie{How do we get from uniquely determined to facet?}
	\item Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
	\item Show that $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$. \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
	\item Note: $\theta(v) = \pi(F_v) \cap \simplex$.
\end{itemize}

>>>>

\jessie{Lemma X}
\begin{lemma}
	Let $f: \simplex \to \reals_+$ be a (concave) polyhedral function.
	There exists a unique set of loss vectors $\V$ of minimum cardinality such that $f(p) = \min_{v \in \V} \inprod{v}{p}$ for all $p\in\simplex$.
	Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V\}$.
	Furthermore, let $L: \R \to \reals^\Y_+$ be any loss whose infimum is attained with Bayes risk $\risk L=f$ and let $\Gamma := \prop{L}$.
	Then $L$ has a finite minimum representative set, and for any minimum representative set $\R^* \subseteq \R$,
	\begin{enumerate}
		\item $\{L(r^*) \mid r^* \in \R^*\} = \V$,
		\item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$\jessie{relative to $\reals^{n-1}$},
		\item For any $r \in \R$, there exists $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$\jessie{power diagrams stuff}.
	\end{enumerate}
\end{lemma}

@@

\begin{itemize}\setlength{\itemsep}{0pt}
	\item By Rockafellar, we have $f$ polyhedral if and only if it can be written as the max of a finite set of linear functions $\hat \V$ over $\reals^\Y_+$.%; outside $\reals^\Y_+$, we take $f$ to be infinite.
	Therefore, $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ over $p \in \reals_+^\Y$.
	%Write $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ for some finite set $\hat\V \subseteq \reals^\Y_+$.    \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar}
	\item We extend $f$ to $g(x) = \min_{v\in\hat\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = \infty$ otherwise, and define $g(0) = 0$.
	That is, $g(x) = \min_{v \in \hat \V} \inprod{x}{v} + \delta(x \mid \reals^\Y_+)$.
	Note that $g$ and $f$ match on $\reals^\Y_+$.
	\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ as the hypograph of $g$.
	\item Let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$ as the set of halfspaces generated by $\hat \V$ and $H_{v} := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c = 0\}$ and as the hyperplanes defining the boundaries of these halfspaces.
	\item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$ as the half spaces generated by the nonnegative orthant and $H_y := \{ (x,c) \in \reals^\Y \times \reals \mid x_y = 0\}$ as the hyperplanes forming the boundary of these halfspaces.
	\item Let $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\hat \V} \cup \H_\Y$.
	\item Then $G = \cap \H$.
	\item Since $G$ is a full-dimensional polyhedron, it has a unique $H$-rep $H'$ uniquely determined by the facets of $G$ by \jessie{Ziegler Theorem 2.15}.
	\item Take $\H' := \{(x,c) \mid \inprod{h'}{x} - c \geq 0\}$ for all $h' \in H'$.
	\item Argue $\H' \subseteq \H$ and $G = \cap \H'$. 
	\jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
	\item Since $G = \cap \H' = \cap (\H_\Y \cup \H_{\hat \V})$, we must have $\H_\Y \subseteq \H'$.
	\item Then $\H' \setminus \H_\Y = \{H_v^+ : v\in\V\} =: \H_\V$ for some $\V \subseteq \hat \V$.
\end{itemize}
	$\V$ is precisely the set we are looking for; it is uniquely generated by $f$ since $\H'$ and $\H_\Y$ are unique, and minimum cardinality since $\H'$ has minimum cardinality.  
	Moreover, $F_v := H_v \cap G$ is a facet of $G$ for each $v\in\V$. \jessie{by analog of Ziegler Theorem 2.15}
	Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
	We claim that $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$. \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
	To see this, observe that any $F_v = H_v \cap G = \{(x,c) \mid \inprod{x}{v} \geq c\} \cap \reals^\Y_+$, so $\cup_{v\in\V} \pi(F_v) \subseteq \reals^\Y_+$.
	Now for any $x \in \reals_+^\Y$, there must be some $v \in \V$ such that $x \in F_v$ by definition of $f$ as the min of linear functions generated by $\V$.
	Note that we can take $\theta(v) = \pi(F_v) \cap \simplex$.
